Type Refinements for the Working Class

### 2015-11-14 paper.tex
Correct mistake in previous commit

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished copresheaf
$\Of{\CanOperators}{\Sets^{\SCtx\times\Discrete{\Arities}}}$ of
\emph{canonical} operators such that $\IsSubsetEq{\CanOperators}{\Operators}$.
For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define the
presheaves of closed expressions and closed values over symbol contexts and sorts as
follows:
\begin{align*}
  \ADefine{\Exprs_\tau(w)}{
    \MkSet{M \mid \IsAbtUnmoded{\cdot}{\pi(w)}{\cdot}{M}{\tau}}
  }\\
  \ADefine{\Values_\tau(w)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(w)\land \exists a. \CanOperators\Pair{\pi(w)}{a}\ni\vartheta
    }
  }
\end{align*}

>>>>

In this section we generalize Howe's notion of lazy computation
system~\cite{howe:1989} to the multi-sorted, symbol-parameterized setting. An
\emph{lazy computation language} is an abt signature
$\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ along with a distinguished copresheaf
$\Of{\CanOperators}{\Sets^{\SCtx\times\Discrete{\Arities}}}$ of
\emph{canonical} operators such that $\IsSubsetEq{\CanOperators}{\Operators}$.
For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define the
presheaves of closed expressions and closed values as follows:
\begin{align*}
  \ADefine{\Exprs_\tau(w)}{
    \MkSet{M \mid \IsAbtUnmoded{\cdot}{\pi(w)}{\cdot}{M}{\tau}}
  }\\
  \ADefine{\Values_\tau(w)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(w)\land \exists a. \CanOperators\Pair{\pi(w)}{a}\ni\vartheta
    }
  }
\end{align*}
